%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NON-INFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES, OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's data for header
\name{Biswambar Pradhan}
\address{Bangalore, \linebreak India}
\contacts{+91 9668089243 \linebreak \mbox{developer.biswambar@gmail.com } \linebreak linkedin.com/in/biswambarp}
\begin{document}

    % Print the header
    \makeheader

    % Print the content
    \begin{cvsection}{Languages and Technologies}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf {Programming Languages and Frameworks:} Java, Spring, Python, Nodejs
                \item \textbf {Cloud Services (AWS):} EC2, ECS Fargate, NLB, S3, Lambda, Glue, Athena, Step Function, Aurora Postgres
                \item \textbf {Infrastructure and Deployment:} CloudFormation, Terraform, Git, Maven, Bamboo, Spinnaker
                \item \textbf {Certifications:} AWS Developer - Associate, AWS Cloud Practitioner
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    \begin{cvsection}{Employment}

        \begin{cvsubsection}{Software Engineer - II}{JP Morgan Chase}{\normalfont 02/2023-Present}
            Financial Transaction Tax Team
            \begin{itemize}
                \item Designed a Financial Transaction Tax application that optimized tax calculations across multiple EU markets (Italy, France, Spain), improving accuracy and compliance.
                \item Developed scalable CRUD REST APIs for trades and exchange rates, leveraging \textbf{Java, Spring Boot, and AWS ECS Fargate}.
                \item Developed a robust currency conversion algorithm utilizing ECB end-of-day exchange rates, ensuring precise conversions across all trades using \textbf{Python}.
                \item Migrated AWS Lambda functions to ECS Tasks through AWS Step Functions for failure-retry mechanisms and SNS-based alerting.
                \item Built APIs and a user interface replicating AWS S3 Console functionalities, using Java, Spring, and React.
                \item Designed daily Batch jobs using \textbf{Python, AWS Glue, Boto3, Athena and Step function} which acts a bulk data source for the application.
                \item Integrated Spinnaker for automated deployment pipelines, reducing deployment time.
                \item Migrated AWS Lambda functions to ECS Tasks, enhancing reliability through AWS Step Functions for failure-retry mechanisms and SNS-based alerting.

            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Software Engineer}{Ernest and Young}{\normalfont 08/2021-02/2023}
            US CDI Team,    Fidelity International
            \begin{itemize}
                \item Built Eligibility Service API in \textbf{Java and Spring Boot} to validate trades within the US CDI platform, ensuring compliance and accuracy.
                \item Developed the Estimation and FX Charge API in \textbf{Java/Spring Boot}, supporting over 2.7 million Fidelity users in US stock purchases.
                \item Created AWS Infrastructure of API gateway and AWS Fargate using CloudFormation in a Blue-Green deployment model.
                \item Created APIs with \textbf{Node.js, Express, and AWS Lambda} to retrieve key financial data from IHS Markit.
                \item Created a Reconciliation application that compares data between 2 sources and sends the discrepancy as a
                Notification (SNS)
                \item US CDI resulted in trading more than £550K in one month.
            \end{itemize}
        \end{cvsubsection}
%
%        \begin{cvsubsection}{Software Engineer}{Persistent Systems}{\normalfont 03/2021-08/2021}
%            Actimize Anti-money Laundering
%            \begin{itemize}
%                \item Built RESTful APIs that served data to our JavaScript front-end that handled over 30,000 concurrent
%                users
%                \item Developed internal tool using Java to automate front-end component creation which reduced development
%                the effort from 3 hrs to 20 minutes
%                \item Created and Managed AWS EC2, RDS instances for the deployment of Microservices
%                \item Interacted with various stakeholders to understand business needs and translate those business needs into
%                actionable features in Java and Spring Boot
%            \end{itemize}
%        \end{cvsubsection}
        \begin{cvsubsection}{Software Engineer}{Tata Consultancy Service}{\normalfont 06/2018 - 03/2021}
            Hospital Beacon Tracker, General Electric
            \begin{itemize}
                \item Implemented an IoT-based tracking system to monitor hospital equipment, resulting in a 30 percent productivity increase.
                \item Migrated over 5 web applications, including servers and databases, from on-premises to \textbf{AWS} Cloud, reducing maintenance costs and enhancing scalability.
                \item Maintained Saleslogix CRM, a legacy product with 200+ daily user engagements, ensuring stability and user satisfaction.
                \item Delivered modules like Tickets, Engagements, and Order Processing within Saleslogix CRM, improving user experience and system functionality.
                \item Migrated all the Application Servers from Windows Server 2003 to Windows Server 2019.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    \begin{cvsection}{Education}
        \begin{cvsubsection}{Bhubaneswar, IN}{\mbox{Odisha University of Technology and Research}}{ (Aug 2014 - May 2018)}
            \begin{itemize}
                \item Bachelor of Technology (B.Tech), Electrical Engineering
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Bhubaneswar, IN}{\mbox{Council of Higher Secondary Education}}{(May 2012 - June 2014)}
            \begin{itemize}
                \item Secondary Education (Physics, Chemistry, Math)
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}


\end{document}